[Re] Speed/accuracy trade-off between the habitual and the goal-directed processes

### 2016-01-20 article/viejo_girard_khamassi.tex
First Submission for Viejo-Khamassi-Girard-2016

\begin{longtable}[c]{@{}lll@{}}
\toprule
Name & Description & Value\tabularnewline
\midrule
\endhead
\(\sigma\) & Updating rate of the average reward & 0.02\tabularnewline
\(\eta\) & Variance of evolution noise & 0.0001\tabularnewline
\(P_n\) & Variance of observation noise & 0.05\tabularnewline
\(\beta\) & Rate of exploration & 1.0\tabularnewline
\(\rho\) & Update rate of the reward function & 0.1\tabularnewline
\(\gamma\) & Discount factor & 0.95\tabularnewline
\(\tau\) & Time step of graph exploration & 0.08\tabularnewline
depth & Depth of search in graph exploration & 3\tabularnewline
\(\phi\) & Update rate of the transition function & 0.5\tabularnewline
init cov & Initialisaton of covariance matrice & 1.0\tabularnewline
\(\kappa\) & Unscentered transform parameters & 0.1\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[c]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Name
\strut\end{minipage} &
\begin{minipage}[b]{0.45\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.27\columnwidth}\raggedright\strut
Value
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
\(\sigma\) \(\eta\) \(P_n\) \(\beta\) \(\rho\) \(\gamma\) \(\tau\) depth
\(\phi\) init cov \(\kappa\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Updating rate of the average reward Variance of evolution noise Variance
of observation noise Rate of exploration Update rate of the reward
function Discount factor Time step of graph exploration Depth of search
in graph exploration Update rate of the transition function
Initialisaton of covariance matrice Unscentered transform parameters
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
0.02 0.0001 0.05 1.0 0.1 0.95 0.08 3 0.5 1.0 0.1
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
